Corporate Security Solutions for BYOD:\\ A Novel User-Centric and Self-Adaptive System

### 2015-07-09 Response to reviewers - r2.tex

Following the Editor's and some of the reviewers' requests, we have updated the state of the art, revising and commenting in the text (Section 2) several works with common topics with this manuscript. The new references can be consulted b the end of this letter.

% -----------------------------------------------------------------------------

\section{Comments by Reviewer \#2}

% Es quotation, no verbatim, øno?
% Antonio - con quotation no se distinguÌa bien el texto del revisor y el de la respuesta. SÛlo hacÌa un sangrado. Creo que asÌ se ve mejor.

@@

\begin{verbatim}
After reviewing the new version of the document, I admit the authors
have  substantially changed section 3 (state of the art) and they have
improved and extended the introduction and sections 4 (description of
the system) and section 5 (comparison with other systems) I
acknowledge the ideas are really interesting and exciting, but I'm
still not sure if the authors are providing new results not published
in their previous works or just rephrasing their text.

Since there is an obvious over-the-top quality in their work and some
good ideas, I'll let the editors decide if the contents are novel
enough (compared to other previous works by the same authors) to be
published in the journal.
\end{verbatim}

We would like to thank the reviewer for his/her opinion and would lead him/her to have another look at the new version, since it has been highly improved.  
As a summary:
%
\begin{itemize}
\item We have described in a more detailed way our previously published papers in this scope (in Section 1), clarifying the differences and contributions of this work with respect to them.
\item Section 2 has been deeply improved adding a much more complete state of the art in the scope of this work. To this end, several works have been read and commented in that section and along the text.
% Antonio - TODO: Fergu, completa esto t˙ que tienes la idea global de lo nuevo en el SotA, por favor.
New references added after the review can be found at the end of this letter.

\item Section 3 has been rewritten in a big part, including a new taxonomy for the analyzed systems at the beginning of the section. Some new tools have been revised and better classified considering the defined taxonomy.
% Antonio - TODO: extender esto de la secciÛn 3 y 5 un poco m·s.

\item The description of MUSES system has been also improved. Several points have been clarified and better explained in Section 4. Moreover, a prototype of the system has been tested in an actual company with success, according to the obtained results. This is explained in the new Section 4.4 (page XX), where the results of some trials are presented.

\item Section 5 has been also completed and enhanced with respect to previous version. It includes a better comparison between MUSES and the rest of tools. Two new tables (1 and 2) have been added summarizing the main features of the systems, for the sake of clarity.

\item A complete proof-editing process has been done, reviewing the English grammar and rewriting several paragraphs for a better comprehension and flow.

\end{itemize}
% Antonio - TODO: AÒadir m·s cosas (medianamente relevantes) que se hayan hecho

These changes are better described in the responses to the others reviewers, so we strongly suggest this reviewer to read them to have a better idea of their impact in the new version of the manuscript.

### 2015-07-09 Response to reviewers - r2.tex

\item Section 5 has been also completed and enhanced with respect to previous version. It includes a better comparison between MUSES and the rest of tools. Two new tables (1 and 2) have been added summarizing the main features of the systems, for the sake of clarity.

\item A complete proof-editing process has been done, reviewing the English grammar and rewriting several paragraphs for a better comprehension and flow.

\end{itemize}
% Antonio - TODO: AÒadir m·s cosas (medianamente relevantes) que se hayan hecho

These changes are better described in the responses to the others reviewers, so we strongly suggest this reviewer to read them in order to have a better idea of their impact in the new version of the manuscript.

### 2015-07-09 MUSES_vs_BYOD_solutions.tex
Cambios en el artículo propuesto por @fergunet
Y un par de correcciones tontas

An example of hands-off method is presented in the work by Gessner et al. \cite{Gessner13userfriendly}. This work mentions the importance of avoiding the modification of the underlying operating system (OS). Therefore, they propose the use of a ``container'' application, installed in the mobile device. This container is able to execute inside it the enterprise applications, acting as a barrier with the rest of the applications, and allowing direct communication with the enterprise VPN. The combination of this method, along cryptographic protocols and time-based sessions, offers a trade-off between security and usability. Also, this method avoids the modification of the underlying kernel of the device. %FERGU: citad este trabajo cuando digáis que es bueno no modificar el OS

@@

On the other hand, the \textit{Non MUSES Aware Apps} are those which MUSES cannot directly interact with. Usually, they can be accessed through the OS. But the type of information to gather from them and also the type of actions to do over them strongly vary depending on the OS. As was already mentioned, when MUSES is not able to close the application, a pop-up feedback message is automatically shown to the user. This message informs about why the action is considered as risky and what the user can do to avoid it.

>>>>

An example of hands-off method is presented in the work by Gessner et al. \cite{Gessner13userfriendly}. This work mentions the importance of avoiding the modification of the underlying operating system (OS). Therefore, they propose the use of a ``container'' application, installed in the mobile device. This container is able to execute inside it the enterprise applications, acting as a barrier with the rest of the applications, and allowing direct communication with the enterprise VPN. The combination of this method, along cryptographic protocols and time-based sessions, offers a trade-off between security and usability. Also, this method avoids the modification of the underlying kernel of the device. %FERGU: citad este trabajo cuando digáis que es bueno no modificar el OS
% Antonio - hecho.

@@

On the other hand, the \textit{Non MUSES Aware Apps} are those which MUSES cannot directly interact with. Usually, they can be accessed through the OS. But the type of information to gather from them and also the type of actions to do over them strongly vary depending on the OS, which should not be modified according to  \cite{Gessner13userfriendly}.
As was already mentioned, when MUSES is not able to close the application, a pop-up feedback message is automatically shown to the user. This message informs about why the action is considered as risky and what the user can do to avoid it.
